%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Trixie}{Roque}{Senior Computer Science Student} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
  \section{about}
    3650 Fairland Blvd.
    Los Angeles, CA 90043
    (323) 547-3780
    ~
    \href{mailto:troque@lion.lmu.edu}{troque@lion.lmu.edu}
    \href{http://github.com/trixr4kdz}{github.com/trixr4kdz}
    \href{http://linkedin.com/in/trixie-roque-b20715a7}{linkedin.com/in/trixie-roque-b20715a7}
  \section{programming languages}
    Java, Python, Matlab, Javascript/HTML/CSS, OCaml, Swift
  \section{relevant courses}
     Data Structures,
     Algorithms,
     Interaction Design,
     Web Applications,
     Computation Theory,
     Computer Systems Design,
     Linear Algebra,
     Programming Languages,
     Computer Graphics,
     Operating Systems,
     Artificial Intelligence
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

  \begin{entrylist}

%------------------------------------------------

    \entry
      {since 2013}
      {Bachelor's of Science {\normalfont in Computer Science}}
      {Loyola Marymount University}
      {Minor {\normalfont in Applied Mathematics} \\ 
      Expected graduation: May 2017 \\
      GPA: 3.81}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

  \begin{entrylist}

%------------------------------------------------

    \entry
      {2016}
      {Center for Computation and Technology}
      {Louisiana State University, Baton Rouge, LA}
      {\emph{Data Analytics Research Assistant} \\
	Created a surrogate reservoir model to optimize waterflooding using IBM predictive statistical tools}
	  
%------------------------------------------------

    \entry
      {2015}
      {Bonanza Media}
      {Los Angeles, CA}
      {\emph{Mobile Game Tester} \\
	Ensured quality of a Shrek-themed slot machine game called Shrek Slots through play-testing}

%------------------------------------------------

    \entry
      {since 2014}
      {LMU Computer Science Department}
      {Loyola Marymount University, Los Angeles, CA}
      {\emph{Computer Science Teaching Assistant} \\
        Assisted underclassmen and graded projects/assignments}

%------------------------------------------------

\end{entrylist}

%------------------------------------------------
%    PROJECTS SECTION
%------------------------------------------------

\section{projects}

  \begin{entrylist}

    \entry
      {2016}
      {Markit}
      {Github}
      {Application to bridge the gap between buyers and sellers in college campuses. Development involved Xcode 8 and Swift 3. Also the group leader for the iOS sub-team to manage tasks for individual members.}

%------------------------------------------------
    
    \entry
      {2016}
      {yah}
      {Github}
      {A statically-typed programming language written in Javascript for CMSI 488 class (Compiler Construction). Features include type inference, list comprehension, higher-order functions, and indentation.}

%------------------------------------------------

    \entry
      {since 2015}
      {GRNmap}
      {Github}
      {Lead developer of a software that simulates gene regulatory networks (written in Matlab). Duties include performing routine bug fixes, adding new features, and enhancing the code base by creating a testing framework and modularizing the source code.}

%------------------------------------------------

    \entry
      {2015}
      {xmlpipedb}
      {Github}
      {Open-source project for BIOL/CMSI 367, which aims to build biological databases using software development tools. Languages used include PostgreSQL and Java.}

%------------------------------------------------
  
  \end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

  \begin{entrylist}
  
%------------------------------------------------

    \shortentry
      {2015}
      {LMU Outstanding Sophomore Student in Computer Science Award}
      
%------------------------------------------------
            
  \end{entrylist}

\end{document}